Weakly informative observations: identifying the weakest player

### 2019-12-08 inst/loser.Rmd
slight copyediting

Now we are going to look at what happens when our observation is only
the _loser_ (which is here taken to be player `a`).  We have six
competitors `a,b,c,d,e,f` with nonnegative strengths
$p_1,p_2,p_3,p_4,p_5,p_6, \sum p_i=1$.  Competitor `a` has strength
$p_1$, and loses.  We are interested in how informative this
observation is with regard to the hypothesis that `a` does in fact
have zero strength.  We have three hypotheses:

@@

In the above, `L` is a likelihood function for the observation that
competitor `a` came last.  In R idiom, it is a list of hyper2 objects
corresponding to all $5!=120$ possible observed order statistics (only
the first two, `L[[1]]` and `L[[2]]`, are printed, which correspond to
orders `bcdefa` and `bcdfea` respectively).  Any order is permissible,
so long as player `a` is bottom.

>>>>

Here we consider a situation in which we make only a rather
uninformative observation: namely, the identity of the _loser_ (which
is here taken to be me, player `a`).  We have six competitors
`a,b,c,d,e,f` with nonnegative strengths $p_1,p_2,p_3,p_4,p_5,p_6,
\sum p_i=1$.  Competitor `a` has strength $p_1$, and loses.  We are
interested in how informative this observation is with regard to
various assertions about the strength of `a`.  We have three
hypotheses:

@@

In the above, `L` is a log-likelihood function for the observation
that competitor `a` came last.  In R idiom, it is a list of hyper2
objects corresponding to all $5!=120$ possible observed order
statistics (only the first two, `L[[1]]` and `L[[2]]`, are printed,
which correspond to orders `bcdefa` and `bcdfea` respectively).  Any
order is permissible, so long as player `a` is bottom.
